Tail associations and their impact on extinction risk

### 2020-01-16 Response.txt

3.      The amount of analyses for metapopulations and age-structured populations seems quite unbalanced. Why is this so? Obviously, the paper would greatly increase its value by including more analyses for stage-structured populations, but then the paper may become too long to fit in the required length for Ecosphere. Would it be more beneficial to focus only on metapopulations in this paper and expand on the stage-structured population part in a separate paper to more deeply examine Tuljapurkar’s approximation?

***Shya: This is our first attempt to introduce the general impact of asymmetric tail-association (using copula) on the extinction risk - be it on the stage-structured model or on the spatial metapopulation models. We agree that further studies are needed as mentioned in the Discussion to examine why those effects are less severe in stage-structured population model compared to the metapopulation - probably we will address that in detail in our 
subsequent papers (I'm not sure about this statement - but I could not think of a better response :P).

4.      The order of appearance of the metapopulation problem and the age-structured population problem keeps switching throughout the paper. For readability, the order should be consistent.

***Shya: Ok, If we assume the accepted order would be first Stage-structured model (Addressing Q1...) and then metapopulation model (addressing Q2...), then I found the reverse order as follows:

In the Introduction: we first explained metapop (para started with "There are also reasons to hypothesize that asymmetry of tail association in environmental...") and then stage structured model (para started with "Extinction risk is also very commonly estimated for age-structured models such as....")

In the Discussion: we first explained the first topic as metapop results and 
then as a second topic stage-structured results (in brief compared to first topic).
Currently, I do not change anything in the maintext, I can rearrange the para but I am afraid in doing so, may be I 
would break the continuation. So, I am leaving for DAN.

@@

***Shya: I have several comments about this criticism:
(i) Reviewer2 has misunderstood us here. Transformation (Linear) does not alter the nature of tail-association, i.e., stronger left tail association remains left-tail dominated, so as for right tail.
(ii) After reading his own story of "good" or "bad" variable - now I'm confused. I think "good" or "bad" notion of variable has nothing to do with the transformation - it is their underlying nature that how they affect the population-size with time. Also, I don't agree that a right tail (or left-tail) association between two contradictory variable (i.e. negatively correlated) nullify the effect on population-extinction risk.
(iii) Our BIVAN paper is now accepted and in press, though not updated in BioRxiv, I am not sure whether I should upload the accepted version in BioRxiv or not because of copyright agreement with Elsevier.

6.      Figure 5 presents cases with d = 0 only and in the appendix different values of d are considered only for global dispersal. Would the results qualitatively hold when different values of d for local dispersal is considered?

***Shya: I personally believe the results should hold, in general, even when d>0 (because d=0 is more stringent case). My goal is to show the crossover happened solely because of the change in dynamical regime, so setting d=0 means there will be no rescue-effect on extinction risk due to metapopulation dispersal. (ok, I checked the simulation result with d=0.3 for local and global dispersal for ricker and hassell, the crossover is around the same r_c, I am attaching the pdfs in my mail).

### 2020-01-16 MainText.Rmd
response edited as of now

<!--ECEs probably produce tail associations-->
There are reasons to hypothesize that ECEs may produce asymmetric tail 
associations between climatic variables
measured in different locations. For instance, suppose a single ECE is associated
with spatially widespread, large values 
of some climatic variable. Also suppose that small values of the
variable are associated, instead, with local weather, which can differ from location
to location, rather than with ECEs. The result could
be stronger right-tail association, through time, between measurements of the climatic variable
made in different locations.
For example, rainstorms which deposit exceptionally large amounts of rain
may do so over large areas. But periods with less rain may experience
scattered showers only, which may be much less correlated across locales.

>>>>

<!--ECEs probably produce tail associations-->

<!--***DAN wrote this-->
<!--There are reasons to hypothesize that ECEs may produce asymmetric tail 
associations between climatic variables
measured in different locations. For instance, suppose a single ECE is associated
with spatially widespread, large values 
of some climatic variable. Also suppose that small values of the
variable are associated, instead, with local weather, which can differ from location
to location, rather than with ECEs. The result could
be stronger right-tail association, through time, between measurements of the climatic variable
made in different locations.
For example, rainstorms which deposit exceptionally large amounts of rain
may do so over large areas. But periods with less rain may experience
scattered showers only, which may be much less correlated across locales.-->

<!--***Shya: I rephrased the following para-->
There are reasons to hypothesize that different locations when influenced by single ECEs may 
show asymmetric tail associations through time. This asymmetry arises because a single 
ECE is associated with spatially widespread, large values 
of some climatic variable whereas small values of the same
variable are associated, instead, with local weather, which can differ from location
to location, rather than with ECEs. For example, rainstorms which deposit 
exceptionally large amounts of rain may do so over large areas. But periods with 
less rain may experience scattered showers only, which may be much 
less correlated across locales. The result could
be stronger right-tail association, through time, between measurements of rainfall
occurred in different locations.
